### 2019-01-26 journal/conclusions.tex
just change format, proofread, and ship

>>>>

More practically, we would like to tightly integrate our approach with
automated test generation tools, such as TSTL \cite{tstlsttt,NFM15},
DeepState \cite{DeepState,DeepStateTutorial}, Echidna \cite{Echidna}, and
Manticore \cite{Manticore}.  Automated test generation tools tend to produce a
large number of passing and failing tests, and are often used in
``overnight'' runs where adding a step to use mutants to triage
failing tests and provide localization suggestions for the highly
ranked tests may not even impose a noticable overhead on current usage
practices.  The latter two tools (Echidna and Manticore), which target smart
contracts for the Ethereum blockchain \cite{wood2014ethereum}, are
particularly promising opportunities, because the gas-limited computation bounds of the Ethereum
Virtual Machine essentially guarantee that smart contract code is
small enough to make mutation analysis cheap.  The availability of a
multi-language mutation analysis tool \cite{RegExpMut} supporting
Python, C/C++, and Solidity (the language used for most smart
contracts) means that a common infrastructure base can be shared by
all of these tool integrations.

### 2019-01-26 journal/experiments.tex
just change format, proofread, and ship

@@

A deterministic alternative to random sampling, long used in the mutation testing community, is operator-based selection, where only some mutation operators are applied \cite{wong1995reducing,untch2009onreduced}.  Using \emph{only statement deletion and condition negation mutants}, as in our toy example, on the grounds that we expect most compiler ``repairs'' to simply avoid an optimization, not actually fix a simple defect such as an off-by-one error in a loop, is an intuitively appealing and trivial to implement approach.  The idea is clearly related to the object-level branch-mutation proposed above, conceptually, but operating at the (more understandable to humans, and thus useful in localization) source level.  The resulting cost reduction is significant:  67.8\% of mutants can be ignored for SpiderMonkey, and 73\% for GCC.  More importantly, the APFD actually \emph{improves} with this change.  For SpiderMonkey, the APFD improves by almost 3\%, and for GCC, it improves by 0.86\%.  For SpiderMonkey, the early curve (first ten items) is improved, and for GCC it is very slightly worse.  Most importantly, in both cases, two additional faults are revealed in the first 50 examined tests.  Operator selection can, in principle (and in one case in our data set, in practice) reduce the effectiveness of fault localization.  However, with hot mutants, it is easy, if localization using only negations and deletions is not helpful, to use the same method as proposed above for random selection to compute a more precise localization for a test.  This should usually not be required, however:  we noted that in most cases where a mutant involved in a localization did use a operator replacement, the mutant was usually equivalent in behavior to a condition negation.  Constant replacement repairs were simply very rare and not involved in any of the useful compiler localizations.  The problem observed with random sampling, that the metric of distances to other tests may be inaccurate, is less of concern with operator selection:  as far as we can tell, based on FPF discovery curves and APFD, distances are \emph{more} accurate using only the mutants we propose.

>>>>

We tried various ways of improving the effectiveness of random sampling by forcing the inclusion of certain mutants that were deemed more likely to be useful.  For example, it is very important to include mutants that repair hard-to-repair faults represented by a small number of tests.  Finding faults represented by few tests is, in some sense, what users want from a fuzzer taming algorithm.  We cannot, without evaluating them over tests, predict which mutants will repair only a small number of tests (and thus, likely, faults with only a few representatives).  However, making sure to include mutants that are only \emph{covered} by a small number of tests lets us ensure we cover mutants that, if they repair any failing tests, only repair a small number of failing tests.  However, due to the likelyhood that such mutants repair no tests at all, including mutants covering at most $k$ tests (for small $k$) turned out to be either actually harmful (statistically significantly worse APFD) or statistically indistinguishable from pure random selection.  We were unable to find any mixes of random and biased or chosen sampling that performed better than pure random sampling.  Is this the best we can do?

@@

A deterministic alternative to random sampling, long used in the mutation testing community, is operator-based selection, where only some mutation operators are applied \cite{wong1995reducing,untch2009onreduced}.  Using \emph{only statement deletion and condition negation mutants}, as in our toy example, on the grounds that we expect most compiler ``repairs'' to simply avoid an optimization, not actually fix a simple defect such as an off-by-one error in a loop, is an intuitively appealing and trivial to implement approach.  The idea is clearly related to the object-level branch-mutation proposed above, conceptually, but operating at the (more understandable to humans, and thus useful in localization) source level.  The resulting cost reduction is significant:  67.8\% of mutants can be ignored for SpiderMonkey, and 73\% for GCC.

More importantly, the APFD actually \emph{improves} with this change.  For SpiderMonkey, the APFD improves by almost 3\%, and for GCC it improves by 0.86\%.  For SpiderMonkey, the early curve (first ten items) is improved, and for GCC it is very slightly worse.  Most importantly, in both cases, \emph{two additional faults} are revealed in the first 50 examined tests.  We speculate that the accidental nature of many repairs produced by operator and constant replacements may introduce harmful noise into the distance metric, and thus the FPF-based fuzzer taming process.  Changes that simply sidestep faulty functionality are, perhaps, more likely to be meaningful \cite{achour}.

Operator selection can, in principle (and in one case in our data set, in practice) reduce the effectiveness of fault localization.  However, with hot mutants, it is easy, if localization using only negations and deletions is not helpful, to use the same method as proposed above for random selection to compute a more precise localization for a test.  This should usually not be required, however:  we noted that in most cases where a mutant involved in a localization did use a operator replacement, the mutant was usually equivalent in behavior to a condition negation.  Constant replacement repairs were simply very rare and not involved in any of the useful compiler localizations.  The problem observed with random sampling, that the metric of distances to other tests may be inaccurate, is of much less concern with operator selection:  as far as we can tell, based on FPF discovery curves and APFD, distances are \emph{more} accurate using only the mutants we propose.

While using only some mutation operators \emph{may} degrade fault localization performance for non-compiler faults, we propose it as the default way to use our approaches in compiler fuzzer taming  and debugging scenarios.  Furthermore, we speculate, based on the results of Qi et al. \cite{achour} showing that most actual correct fixes in program repair are functionality deletions, that limiting mutants used to condition negations and statement deletions (or even adding an operator that converts conditionals to a {\tt False} constant, as is provided by some tools \cite{RegExpMut}), might be the best practice for complex programs and ``deep'' (hard to debug) faults in general.  It seems unlikely that mutation operators will produce many fixes that do not simply avoid broken functionality (vs. actually fix it), for the kinds of faults that are actually hard for programmers to locate, understand, and correct.
